---
title: "NSAIDS in pregnancy - all"
author: "Ariel A Hasidim"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    code_download: true
    toc: yes
    number_sections: yes
    toc_float: yes
    toc_collapsed: yes
    toc_depth: 3
    theme: simplex
---
# Meta
## setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(dpi=300,fig.width=7)
knitr::opts_chunk$set(warning = TRUE, message = TRUE) 

set.seed(54321)

# Installs pacman ("package manager") if needed
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  pacman,
  tidyverse,
  ggsci,
  readr,
  gtsummary,
  readxl,
  labelled,
  MatchIt,
  marginaleffects,
  gt,
  gtExtras,
  tidysmd,
  AER,
  cards,
  UpSetR
) 
```

## wrangling
```{r data, include=FALSE}
##### GET DATA
raw_df <- read.csv('./NSAIDS_Other_Antipyretics_Sensitivity.csv') %>%
  left_join(read.csv('./paracetamol id.csv'), by = "AdminNum") %>%
  left_join(read.csv('./dipyron id.csv'), by = "AdminNum") %>%
  left_join(read.csv('./indication id.csv'), by = "AdminNum") %>%
  replace_na(list(
    Musculoskeletal = 0,
    Pain.Inflammatory = 0,
    Injury.Fracture = 0,
    Pregnancy.related = 0,
    Fever.Infection = 0
  ))

# assigning labels from csv file
metadata <- read_excel("metadata.xlsx") |> deframe()

##### DATA WRANGLING
# df <- raw_df %>% select(

clean_df <- raw_df %>%
  mutate(
    MPatientIdentity = if_else(
      is.na(MPatientIdentity),
      AdminNum+30000000,
      MPatientIdentity
    ),
    Congenital_Malformations_Major = if_else(
      is.na(Congenital_Malformations_Major),
      if_else(
        CVS_Malformations +
          MSK_Malformations +
          NEURO_Malformations +
          CleftPalate_Malformations +
          GI_Malformations +
          UG_Malformations > 0,
        1,
        0
      ),
      Congenital_Malformations_Major
    ),
    SexCode = case_when(SexCode == "Male" ~ 1, SexCode == "Female" ~ 0, .default = NA),
    Diabetes = replace_na(Diabetes, 0),
    pregestational_diabetes = if_else((Diabetes == 1) &
                                        (Gestational_Diabetes == 0), 1, 0),
    Smoker = replace_na(Smoker, 0),
    LOPC = replace_na(LOPC, 0),
    PregnancyTermination = as.integer(PregnancyTermination),
    BirthYearGroup = cut(
      BirthTerminationYear,
      breaks = seq(1998, 2017 + 1, by = 5),
      right = FALSE,
      labels = c("1998–2002", "2003–2007", "2008–2012", "2013–2017")
    ),
    Mom_Age_Group = cut(
      Mom_Age,
      breaks = c(-Inf, 19, 24, 29, 34, 39, 44, Inf),
      right = TRUE,
      labels = c("<20", "20–24", "25–29", "30–34", "35–39", "40–44", "≥45")
    ),
    first_trimester_exposure_any = (
      if_else(
        first_trimester_exposure_Ibuprofen + first_trimester_exposure_Diclofenac +
          first_trimester_exposure_Naproxen + first_trimester_exposure_Indometacin +
          first_trimester_exposure_Etodolac + first_trimester_exposure_Piroxicam +
          first_trimester_exposure_Lornoxicam > 0,
        1,
        0
      )
    ),
    first_trimester_exposure_any_lbl = if_else(first_trimester_exposure_any == 0, "Unexposed", "NSAIDS"),
    first_trimester_exposure_other_antipyretics = if_else(first_trimester_exposure_Paracetamol + first_trimester_exposure_Dipyrone > 0, 1, 0),
    PregnancyNum = if_else(PregnancyNum > 25, NA, PregnancyNum),
    first_trimester_ddd_any = pmax(
      first_trimester_DDD_Ibuprofen,
      first_trimester_DDD_Diclofenac,
      first_trimester_DDD_Naproxen,
      first_trimester_DDD_Indometacin,
      first_trimester_DDD_Etodolac,
      first_trimester_DDD_Piroxicam,
      first_trimester_DDD_Lornoxicam
    ),
    ddd_class_any = factor(
      case_when(
        first_trimester_ddd_any > 21 ~ 3,
        first_trimester_ddd_any > 7 ~ 2,
        first_trimester_ddd_any >= 1 ~ 1,
        .default = 0
      )
    )
  )

clean_df <- clean_df |> 
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

clean_df_excluded <- clean_df %>%
  transmute(
    first_trimester_exposure_any,
    first_trimester_exposure_any_lbl,
    MPatientIdentity,
    first_trimester_exposure_Paracetamol,
    first_trimester_exposure_Dipyrone,
    first_trimester_exposure_other_antipyretics,
    other_antipyretics_before_NSAIDs,
    other_antipyretics_after_NSAIDs,
    New_MomAge,
    Mom_Age,
    Mom_Age_Group,
    Bedouin,
    pregnancy_termination,
    LOPC,
    PregnancyAge_Final,
    Smoker,
    Diabetes,
    pregestational_diabetes,
    Gestational_Diabetes,
    SexCode,
    NSAID_indication,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations,
    Perinatal_Death,
    PregnancyTermination,
    BirthTerminationYear,
    BirthYearGroup,
    LBW,
    VLBW,
    Apgar1,
    Apgar5,
    InfantWeigth,
    PregnancyNum,
    obesity,
    folic_acid,
    fertilitytx,
    insemination,
    ivf
  ) %>%
  drop_na(
    Mom_Age,
    Bedouin,
    PregnancyNum,
    LOPC,
    NSAID_indication,
    BirthTerminationYear,
    Diabetes,
    obesity,
    folic_acid,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations
  )

clean_df_excluded <- clean_df_excluded |> 
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)
```

## functions
```{r functions}
est_ci <- function(est, low, high) {
  paste0(round(est, 2), " [", round(low, 2), ", ", round(high, 2), "]")
}

rr_summery_cus <- function(
    exposure,                       # bare column (e.g., first_trimester_exposure_Ibuprofen)
    outcome,                        # bare column (e.g., Congenital_Malformations_Major)
    vars,                           # character vector of adjustment terms
    data,                           # data.frame / tibble
    family = poisson(link = "log"),
    unexposed_label = "unexposed",
    exposed_label   = "nsaids",
    wts_col = "weights",
    cluster_col = NA
) {
  expo <- deparse1(substitute(exposure))
  outc <- deparse1(substitute(outcome))

  # label fallback
  out_label <- tryCatch({
    lab <- labelled::var_label(data[[outc]])
    if (is.null(lab) || identical(lab, "")) outc else as.character(lab)
  }, error = function(e) outc)

  # --- helpers ---
  expo_factorize <- function(df, prefix, pred_df) {
    pred_df %>%
      transmute(
        "{expo}" := .data[[expo]],
        .grp = if_else(.data[[expo]] == 0, unexposed_label, exposed_label),
        "{prefix}_incidence"      := estimate * 1000,
        "{prefix}_incidence_low"  := conf.low * 1000,
        "{prefix}_incidence_high" := conf.high * 1000
      ) %>%
      select(.grp, starts_with(paste0(prefix, "_"))) %>%
      pivot_wider(
        names_from = .grp,
        values_from = c(
          any_of(paste0(prefix, c("_incidence","_incidence_low","_incidence_high")))
        )
      )
  }

  rr_cols <- function(prefix, cmp_df) {
    cmp_df %>%
      transmute(
        "{prefix}_rr"      := estimate,
        "{prefix}_rr_low"  := conf.low,
        "{prefix}_rr_high" := conf.high
      )
  }

  # --- formulas ---
  f_unadj <- reformulate(expo, response = outc)
  f_adj   <- reformulate(c(expo, vars), response = outc)

  # --- 1) Unadjusted ---
  fit_unadj <- glm(f_unadj, data = data, family = family)

  pred_unadj <- avg_predictions(fit_unadj, variables = expo)
  cmp_unadj  <- avg_comparisons(fit_unadj, variables = expo, comparison = "lnratioavg", transform = "exp")

  out_tbl <- bind_cols(
    expo_factorize(data, "unadj", pred_unadj),
    rr_cols("unadj", cmp_unadj)
  )

  # --- 2) Adjusted ---
  fit_adj <- glm(f_adj, data = data, family = family)

  pred_adj <- avg_predictions(fit_adj, variables = expo, type = "response")
  
  cmp_adj  <- avg_comparisons(
    fit_adj,
    variables = expo,
    type = "response",
    comparison = "lnratioavg",
    transform = "exp",
    vcov = if (is.na(cluster_col)) "HC3" else as.formula(paste0("~", cluster_col))
  )
  
  out_tbl <- out_tbl %>%
    bind_cols(
      expo_factorize(data, "adj", pred_adj),
      rr_cols("adj", cmp_adj)
    )

  # --- 3) Adjusted + weights (if available) ---
  has_w <- (wts_col %in% names(data))
  has_c <- (!is.na(cluster_col))

  if (has_w) {
    fit_w <- glm(f_adj, data = data, family = family, weights = data[[wts_col]])
    vcov_arg <- if (has_c) as.formula(paste0("~subclass + ", cluster_col)) else ~subclass

    pred_w <- avg_predictions(
      fit_w,
      variables = expo,
      type = "response",
      vcov = vcov_arg,
      wts  = if (has_c) FALSE else wts_col
    )

    cmp_w <- avg_comparisons(
      fit_w,
      variables = expo,
      type = "response",
      comparison = "lnratioavg",
      transform = "exp",
      vcov = vcov_arg,
      wts  = if (has_c) FALSE else wts_col
    )
    
    out_tbl <- out_tbl %>%
      bind_cols(
        expo_factorize(data, "adj_wts", pred_w),
        rr_cols("adj_wts", cmp_w)
      )
  } else {
    empty_w <- tibble(
      adj_wts_incidence_unexposed = NA_real_,
      adj_wts_incidence_nsaids    = NA_real_,
      adj_wts_incidence_low_unexposed = NA_real_,
      adj_wts_incidence_low_nsaids    = NA_real_,
      adj_wts_incidence_high_unexposed = NA_real_,
      adj_wts_incidence_high_nsaids    = NA_real_,
      adj_wts_rr = NA_real_,
      adj_wts_rr_low = NA_real_,
      adj_wts_rr_high = NA_real_
    )
    out_tbl <- bind_cols(out_tbl, empty_w)
  }

  out_tbl %>% mutate(malformation = out_label)
}
```

# Population

## Table1
```{r}
table1 <- clean_df %>%
  transmute (
    first_trimester_exposure_any_lbl,
    BirthTerminationYear = BirthYearGroup,
    Mom_Age = Mom_Age_Group,
    Bedouin,
    obesity,
    Smoker,
    Diabetes,
    NSAID_indication,
    first_trimester_exposure_other_antipyretics,
    PregnancyNum,
    PregnancyAge_Final,
    fertilitytx,
    insemination,
    ivf,
    LOPC,
    folic_acid,
    SexCode,
    pregnancy_termination,
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c() ~ "continuous",
      c(BirthTerminationYear, Mom_Age) ~ "categorical",
      c(
        Bedouin,
        Smoker,
        Diabetes,
        SexCode,
        LOPC,
        pregnancy_termination,
        NSAID_indication,
        obesity,
        folic_acid,
        fertilitytx,
        insemination,
        ivf,
        first_trimester_exposure_other_antipyretics
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(PregnancyAge_Final, PregnancyNum) ~ "{median} ({p25}, {p75})"
    ),
    missing = "ifany",
    missing_text = "Missing"
  )  %>%
  add_p() %>%
  bold_labels() %>%
  modify_indent(columns = label,
                rows = variable %in% c("insemination", "ivf"))

table1
```


## NSAIDs and Other Antipyretics exposures and intersections

UpSetR generates static UpSet plots. The UpSet technique visualizes set intersections in a matrix layout and introduces aggregates based on groupings and queries. 

```{r}
clean_df %>%
  transmute(
    Ibuprofen   = as.integer(first_trimester_exposure_Ibuprofen),
    Diclofenac  = as.integer(first_trimester_exposure_Diclofenac),
    Naproxen    = as.integer(first_trimester_exposure_Naproxen),
    Indometacin = as.integer(first_trimester_exposure_Indometacin),
    Etodolac    = as.integer(first_trimester_exposure_Etodolac),
    Piroxicam   = as.integer(first_trimester_exposure_Piroxicam),
    Lornoxicam  = as.integer(first_trimester_exposure_Lornoxicam),
    "Other Antipyretics" = first_trimester_exposure_other_antipyretics
  ) %>%
  UpSetR::upset(
  sets = c("Other Antipyretics", "Ibuprofen", "Diclofenac","Naproxen","Etodolac","Indometacin","Piroxicam","Lornoxicam"),
  nsets = 0,
  nintersects = 10,        # כמה שילובים להציג
  order.by = "freq",
  decreasing = TRUE,
  mb.ratio = c(0.6, 0.4),  # יחס בין main bars ל-set size bars
  empty.intersections = "off"
  # ,
  #   queries = list(
  #   list(
  #     query = intersects,
  #     params = "Other Antipyretics",
  #     color = "orange",
  #     active = TRUE
  #   )
  # )
)
```


## Annual exposure rates

```{r}
clean_df %>%
  transmute(
    BirthTerminationYear,
    first_trimester_exposure_Ibuprofen,
    first_trimester_exposure_Diclofenac,
    first_trimester_exposure_Naproxen,
    first_trimester_exposure_Indometacin,
    first_trimester_exposure_Etodolac,
    first_trimester_exposure_Piroxicam,
    first_trimester_exposure_Lornoxicam
  ) %>%
  summarise(
    .by = BirthTerminationYear,
    Ibuprofen = mean(first_trimester_exposure_Ibuprofen) * 100000,
    Diclofenac = mean(first_trimester_exposure_Diclofenac) * 100000,
    Naproxen = mean(first_trimester_exposure_Naproxen) * 100000,
    Indometacin = mean(first_trimester_exposure_Indometacin) * 100000,
    Etodolac = mean(first_trimester_exposure_Etodolac) * 100000,
    Piroxicam = mean(first_trimester_exposure_Piroxicam) * 100000,
    Lornoxicam = mean(first_trimester_exposure_Lornoxicam) * 100000
  ) %>%
  pivot_longer(!BirthTerminationYear,
               names_to = "nsaid",
               values_to = "exposure") %>%
  mutate(nsaid = factor(
    nsaid,
    levels = c(
      "Ibuprofen",
      "Diclofenac",
      "Naproxen",
      "Indometacin",
      "Etodolac",
      "Piroxicam",
      "Lornoxicam"
    )
  )) %>%
  ggplot(aes(
    x = BirthTerminationYear,
    y = exposure,
    color = nsaid,
    group = nsaid
  )) +
  geom_line(aes(linetype = nsaid), linewidth = 1) +
  geom_point(aes(shape = nsaid), size = 2) +
  labs(
    x = "Year of Birth/Termination",
    y = "Exposures per 100,000 pregnancies",
    color = "NSAID",
    linetype = "NSAID",
    shape = "NSAID"
  ) +
  scale_color_nejm() +
  theme_classic()
```

## NSAIDs indication breakdown

```{r}
nsaid_indication_tbl <- clean_df %>%
  select (
    first_trimester_exposure_any_lbl,
    Musculoskeletal,
    Pain.Inflammatory,
    Injury.Fracture,
    Pregnancy.related,
    Fever.Infection
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c() ~ "continuous",
      c() ~ "categorical",
      c(
        Musculoskeletal,
        Pain.Inflammatory,
        Injury.Fracture,
        Pregnancy.related,
        Fever.Infection
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c() ~ "{median} ({p25}, {p75})"
    ),
    missing = "ifany",
    missing_text = "Missing"
  )  %>%
  add_p() %>%
  bold_labels()

nsaid_indication_tbl
```

## Table2

```{r}
table2 <- clean_df %>%
  select(
    first_trimester_exposure_any_lbl,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations,
    PregnancyTermination,
    Perinatal_Death
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c() ~ "continuous",
      c() ~ "categorical",
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations,
        PregnancyTermination,
        Perinatal_Death
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c() ~ "{median} ({p25}, {p75})"
    ),
    missing = "no"
  ) %>%
  add_n() %>%
  add_p()

table2
```

## Multivar for "Major Malformations", no matching

### Assesing overdispersion:

This is the the source for the method with refrences:

-   <https://stats.stackexchange.com/a/66593/323174>

```{r}
# For poisson model
rd <- glm(Congenital_Malformations_Major ~ 1, data = clean_df, family = poisson(link = "log"))
dispersiontest(rd,trafo=1) # should have insignificant p-value
```

### Poisson with log link 

summary:

```{r}
m1.fit <-
  glm(
    Congenital_Malformations_Major ~ first_trimester_exposure_any +
    BirthTerminationYear +
    I(BirthTerminationYear ^ 2) +
    Mom_Age + 
    LOPC +
    Bedouin + 
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker +
    first_trimester_exposure_other_antipyretics,
    data = clean_df,
    family = poisson(link = "log") # account for OVERDISPERSION in BINARY outcome
  )

summary(m1.fit)
```

full regression (exponentiated = OR):
```{r}
tbl_regression(m1.fit, exponentiate = TRUE)
```

marginal RR effect: <!-- <= botton line -->

```{r}
avg_comparisons(
  m1.fit,
  variables = "first_trimester_exposure_any",
  type = "response", # <- doesnt make any change
  comparison = "lnratioavg",
  transform = "exp",
  vcov = ~MPatientIdentity
)
```

## DDD

### Table1
```{r}
table1_ddd <- clean_df %>%
  select(
    ddd_class_any,
    BirthYearGroup,
    Mom_Age_Group,
    Bedouin,
    obesity,
    Smoker,
    Diabetes,
    NSAID_indication,
    first_trimester_exposure_other_antipyretics,
    PregnancyNum,
    PregnancyAge_Final,
    fertilitytx,
    insemination,
    ivf,
    LOPC,
    folic_acid,
    SexCode,
    pregnancy_termination,
  ) %>%
  tbl_summary(
    by = ddd_class_any,
    type = list(
      c() ~ "continuous",
      c(BirthYearGroup, Mom_Age_Group) ~ "categorical",
      c(
        Bedouin,
        Smoker,
        Diabetes,
        SexCode,
        LOPC,
        pregnancy_termination,
        NSAID_indication,
        obesity,
        folic_acid,
        fertilitytx,
        insemination,
        ivf,
        first_trimester_exposure_other_antipyretics
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(PregnancyAge_Final, PregnancyNum) ~ "{median} ({p25}, {p75})"
    ),
    missing = "ifany",
    missing_text = "Missing"
  )  %>%
  add_p(
    test = list(
      all_continuous() ~ "kruskal.test",
      all_categorical() ~ "fisher.test"
    ),
    test.args = list(
      all_tests("fisher.test") ~ list(simulate.p.value = TRUE, B = 10000)
    )
  )

table1_ddd
```

### Analysis

```{r}
m.fit <-
  glm(
    Congenital_Malformations_Major ~ ddd_class_any + 
    BirthTerminationYear +
    I(BirthTerminationYear ^ 2) +
    Mom_Age + 
    LOPC +
    Bedouin + 
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker +
    first_trimester_exposure_other_antipyretics,
    data = clean_df,
    family = poisson(link = "log")
  )

rx <- "mean\\((\\d+)\\)\\s*/\\s*mean\\(0\\)"

ddd_rr_df <- avg_comparisons(
      m.fit,
      variables  = "ddd_class_any",
      type = "response",
      comparison = "lnratioavg",
      transform = "exp",
      vcov = ~MPatientIdentity
    ) %>%
      as.data.frame() %>%
      transmute(
        class = str_match(contrast, rx)[, 2],
        estimate = estimate,
        p.value  = p.value,
        conf.low = conf.low,
        conf.high = conf.high
      ) %>%
      bind_rows(
        tibble(
          class = "0",
          estimate = 1,
          `2.5 %` = NA_real_,
          `97.5 %` = NA_real_,
          `Pr(>|z|)` = NA_real_
        )
      )

ddd_table <- clean_df %>%
  select(Congenital_Malformations_Major, ddd_class_any) %>%
  summarise(
    .by = ddd_class_any,
    n = sum(Congenital_Malformations_Major == 1, na.rm = TRUE),
    total = sum(!is.na(Congenital_Malformations_Major)),
    pct   = 100 * n / total,
    label = sprintf("%d/%d (%.1f%%)", n, total, pct)
  ) %>%
  transmute(class = ddd_class_any, Congenital_Malformations_Major = label) %>%
  left_join(ddd_rr_df,
  by = join_by(class)) %>%
  arrange(class) %>%
  transmute(
    class = case_when(
      class == 3 ~ ">21",
      class == 2 ~ "8-21",
      class == 1 ~ "1-7",
      class == 0 ~ "None"
    ),
    Congenital_Malformations_Major,
    aRR = est_ci(estimate, conf.low, conf.high)
  ) %>%
  gt() %>%
  cols_label(
    class = "Total DDD for NSAIDs",
    Congenital_Malformations_Major = "Major Congenital Malformations",
    aRR = "Adjusted RR (%95 CI)"
  )

ddd_table
```

# Matched Cohort

## Matching

```{r}
# Mahalanobis distance, 1:1 nearest neighbor matching with no replacement
m.out <- matchit(
  first_trimester_exposure_any ~ 
    BirthTerminationYear +
    I(BirthTerminationYear ^ 2) +
    Mom_Age + 
    LOPC +
    Bedouin + 
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker +
    first_trimester_exposure_other_antipyretics,
  data = clean_df_excluded,
  method = "quick",
  estimand = "ATE"
)

m.data <- match.data(m.out) |>
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

ess_treated  <- formatC(cobalt::bal.tab(m.out, un = FALSE)$Observations["Matched (ESS)", "Treated"],  format = "f", digits = 0, big.mark = ",")
ess_control  <- formatC(cobalt::bal.tab(m.out, un = FALSE)$Observations["Matched (ESS)", "Control"],  format = "f", digits = 0, big.mark = ",")
```

## Assessing the Quality Excluded and Matched Cohort

Model specifications:

```{r}
m.out
```

Summary:

```{r, cache=TRUE}
# Checking balance before and after matching:
m.summary <- summary(m.out)

m.summary
```


### Love Plot

```{r, cache=TRUE}
# Plot balance
cobalt::love.plot(m.out, binary = "std", thresholds = c(m = .1))
```

## Table 1

```{r}
# Variables of interest
vars <- c(
  "first_trimester_exposure_any",
  "Mom_Age",
  "Bedouin",
  "PregnancyNum",
  "LOPC",
  "Diabetes",
  "SexCode",
  "pregnancy_termination",
  "BirthTerminationYear",
  "NSAID_indication",
  "obesity",
  "folic_acid",
  "Smoker",
  "SexCode",
  "pregestational_diabetes",
  "fertilitytx",
  "insemination",
  "ivf",
  "PregnancyAge_Final",
  "first_trimester_exposure_other_antipyretics"
)

# SMDs before matching
smds <- tidy_smd(
  .df = m.data,
  .vars = vars,
  .group = first_trimester_exposure_any,
  .wts = weights,
  include_observed = TRUE,
  na.rm = TRUE
) %>%
  select(-first_trimester_exposure_any) %>%
  pivot_wider(names_from = method, values_from = smd) %>%
  mutate(
    before = abs(observed),
    after = abs(weights),
    .keep = "unused"
  )

tbl1 <- m.data %>%
  transmute (
    first_trimester_exposure_any_lbl,
    BirthTerminationYear = BirthYearGroup,
    Mom_Age = Mom_Age_Group,
    Bedouin,
    obesity,
    Smoker,
    Diabetes,
    NSAID_indication,
    first_trimester_exposure_other_antipyretics,
    PregnancyNum,
    PregnancyAge_Final,
    fertilitytx,
    insemination,
    ivf,
    LOPC,
    folic_acid,
    SexCode,
    pregnancy_termination,
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c() ~ "continuous",
      c(BirthTerminationYear, Mom_Age) ~ "categorical",
      c(
        Bedouin,
        Smoker,
        Diabetes,
        SexCode,
        LOPC,
        pregnancy_termination,
        NSAID_indication,
        obesity,
        folic_acid,
        fertilitytx,
        insemination,
        ivf,
        first_trimester_exposure_other_antipyretics,
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(PregnancyAge_Final, PregnancyNum) ~ "{median} ({p25}, {p75})"
    ),
    missing = "ifany",
    missing_text = "Missing"
  )  %>%
  add_p() %>%
  bold_labels() %>%
  modify_table_body(
    ~ .x %>%
      left_join(smds, by = "variable") %>%
      mutate(
        smd_before = if_else(row_type == "label", if_else(is.na(before), "", as.character(round(
          before, 2
        ))), ""),
        smd_after = if_else(row_type == "label", if_else(is.na(after), "", as.character(round(
          after, 2
        ))), "")
      )
  ) %>%
  modify_header(smd_before ~ "**aSMD before**", smd_after ~ "**aSMD after**") %>%
  modify_indent(columns = label,
                rows = variable %in% c("insemination", "ivf")) %>%
  modify_footnote_body(
    footnote = "Covariates included in adjusted models",
    columns = "label",
    rows = variable %in% c(
      "BirthTerminationYear",
      "Mom_Age",
      "LOPC",
      "Bedouin",
      "NSAID_indication",
      "Diabetes",
      "PregnancyNum",
      "obesity",
      "folic_acid",
      "Smoker",
      "first_trimester_exposure_other_antipyretics"
    )
    & row_type == "label"
  ) %>%
  as_gt() %>%
  opt_footnote_marks(marks = c("1", "2", "*")) %>%
  tab_source_note(
    source_note = md(
      "aSMD, absolute Standardized Mean Difference; ATE, Average Treatment Effect; ESS, Effective Sample Size; NSAIDS, Nonsteroidal anti-inflammatory drugs; Tx, Treatment."
    )
  )  %>%
  tab_source_note(source_note = md(
    paste0(
      "ESS for matching-adjusted model targeting the ATE were ",
      ess_treated,
      " exposed and ",
      ess_control,
      " controls. No actual units were discarded during the proccess."
    )
  )) %>%
  tab_source_note(
    source_note = md(
      "Maternal obesity was defined using ICD-9 codes 278.0–278.4, diabetes using ICD-9 250.* and gestational diabetes (GDM) 648.00–648.04, and folic acid use as dispensation during the first trimester. Maternal smoking was based on self-report or ICD-9 code 305.1. Exposure to other analgesics or antipyretics was defined as first-trimester exposure to either acetaminophen or dipyrone. NSAID indications were defined as first-trimester diagnoses for conditions commonly treated with NSAIDs, including musculoskeletal/joint disorders, pain and inflammatory conditions, injuries/fractures, and pregnancy-related diagnoses such as threatened abortion or fever/infection. Gravidity refers to total prior pregnancies. "
    )
  ) %>%
  tab_source_note(
    source_note = md(
      "Missing values for fetal sex reflect pregnancy terminations due to suspected fetal malformations, for which fetal sex could not be determined."
    )
  ) %>%
  tab_source_note(
    source_note = md(
      "SMDs for *Calendar year of birth* were calculated using the ordinal calendar year variable; grouped categories are shown for presentation purposes only."
    )
  )

tbl1
```

### Gravidity - difference measure with its confidence interval


```{r}
m.fit.gravity <- glm(PregnancyNum ~ first_trimester_exposure_any_lbl, data = m.data, family = poisson("log"))

avg_comparisons(
  m.fit.gravity,
  variables  = "first_trimester_exposure_any_lbl",
  type       = "response",      # על סקאלת COUNT
  comparison = "difference"     # E[Y|1] - E[Y|0]
)
```

## Table 2 (simple)

```{r}
tbl2_simple <- m.data %>%
  select(
    first_trimester_exposure_any_lbl,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations,
    Perinatal_Death,
    LBW,
    VLBW,
    Apgar1,
    Apgar5,
    InfantWeigth
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c(InfantWeigth) ~ "continuous",
      c() ~ "categorical",
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations,
        Perinatal_Death,
        LBW,
        VLBW,
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(Apgar1, Apgar5) ~ "{median} ({p25}, {p75})"
    ),
    missing = "no"
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  add_n()

tbl2_simple
```

## Table 2 - Full adjusted for all systemic malformations

```{r}
vars_rr <- c(
  "BirthTerminationYear",
  "I(BirthTerminationYear ^ 2)",
  "Mom_Age",
  "LOPC",
  "Bedouin",
  "NSAID_indication",
  "Diabetes",
  "PregnancyNum",
  "obesity",
  "folic_acid",
  "Smoker",
  "first_trimester_exposure_other_antipyretics"
)


maj_df <- rr_summery_cus(
  first_trimester_exposure_any,
  Congenital_Malformations_Major,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

cvs_df <- rr_summery_cus(
  first_trimester_exposure_any,
  CVS_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

msk_df <- rr_summery_cus(
  first_trimester_exposure_any,
  MSK_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

neuro_df <- rr_summery_cus(
  first_trimester_exposure_any,
  NEURO_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

clp_df <- rr_summery_cus(
  first_trimester_exposure_any,
  CleftPalate_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

gi_df <- rr_summery_cus(
  first_trimester_exposure_any,
  GI_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

gu_df <- rr_summery_cus(
  first_trimester_exposure_any,
  UG_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)
```

### Fill In
```{r}
tbl2 <- m.data %>%
  select(
    first_trimester_exposure_any_lbl,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations
      ) ~ "dichotomous"
    ),
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  )


tbl2_df <- tbl2 %>% as.data.frame()

names(tbl2_df)[1] <- "malformation"

tbl2_df <- tbl2_df %>%
  left_join((
    bind_rows(maj_df, cvs_df, msk_df, neuro_df, clp_df, gi_df, gu_df)
  ), by = "malformation")



table2_for_print <- tbl2_df
names(table2_for_print)[2] <- "cases_nsaids"
names(table2_for_print)[3] <- "cases_unexposed"

gt(
  table2_for_print %>%
    transmute(
      malformation,
      cases_unexposed,
      unadj_incidence_unexposed_conj = est_ci(
        unadj_incidence_unexposed,
        unadj_incidence_low_unexposed,
        unadj_incidence_high_unexposed
      ),
      cases_nsaids,
      unadj_incidence_nsaids_conj = est_ci(
        unadj_incidence_nsaids,
        unadj_incidence_low_nsaids,
        unadj_incidence_high_nsaids
      ),
      unadj_rr_conj = est_ci(unadj_rr, unadj_rr_low, unadj_rr_high),
      adj_rr_conj = est_ci(adj_rr, adj_rr_low, adj_rr_high),
      adj_wts_rr_conj = est_ci(adj_wts_rr, adj_wts_rr_low, adj_wts_rr_high),
      adj_wts_rr,
      adj_wts_rr_low,
      adj_wts_rr_high
    ),
  rowname_col = "malformation"
) |>
  cols_label(
    malformation = md("**Malformation**"),
    cases_nsaids = "Events",
    unadj_incidence_nsaids_conj = "Events/1000 (95% CI)",
    cases_unexposed = "Events",
    unadj_incidence_unexposed_conj = "Events/1000 (95% CI)",
    unadj_rr_conj = "Unadjusted",
    adj_rr_conj = "Adjusted",
    adj_wts_rr_conj = "Matched Adjusted",
    adj_wts_rr = ""
  ) |>
  tab_style(style = cell_text(align = "center"),
            locations = cells_column_labels(columns = everything())) |>
  tab_spanner(
    label = md(paste0(
      "**Unexposed** <br>(N=", table(tbl2$inputs$data[[tbl2$inputs$by]])[2], ")"
    )),
    columns = c(cases_unexposed, unadj_incidence_unexposed_conj)
  ) |>
  tab_spanner(
    label = md(paste0(
      "**NSAID** <br>(N=", table(tbl2$inputs$data[[tbl2$inputs$by]])[1], ")"
    )),
    columns = c(cases_nsaids, unadj_incidence_nsaids_conj)
  ) |>
  tab_spanner(
    label = md("**RR** [95% CI]"),
    columns = c(unadj_rr_conj, adj_rr_conj, adj_wts_rr_conj, adj_wts_rr)
  ) |>
  cols_align(
    align = "left",
    columns = c(
      cases_unexposed,
      unadj_incidence_unexposed_conj,
      cases_nsaids,
      unadj_incidence_nsaids_conj,
      unadj_rr_conj,
      adj_rr_conj,
      adj_wts_rr_conj
    )
  ) |>
  tab_stub_indent(
    rows = c(
      "Cardiovascular",
      "Musculoskeletal",
      "Cleft palate",
      "Central nervous system",
      "Gastrointestinal",
      "Genitourinary"
    ),
    indent = 3
  ) |>
  tab_options(table.width = px(1400)) |>
  fmt_number(drop_trailing_zeros = FALSE) |>
  gt_plt_conf_int(
    adj_wts_rr,
    c(adj_wts_rr_low, adj_wts_rr_high),
    ref_line = 1,
    text_size = 0,
    palette = c("black", "darkgrey", "black", "black")
  ) |>
  cols_hide(columns = c(adj_wts_rr_low, adj_wts_rr_high))
```

# Sensetivity Analysis for other antipyretics

## removing other antipyretics from model

### matching 

```{r wrangling removing other anypiretics and matching}
m.out1 <- matchit(
  first_trimester_exposure_any ~
    BirthTerminationYear +
    I(BirthTerminationYear^2) +
    Mom_Age +
    LOPC +
    Bedouin +
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker,
  data = clean_df_excluded,
  method = "quick",
  estimand = "ATE"
)

m.data1 <- match.data(m.out1) |>
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

ess_treated1  <- formatC(cobalt::bal.tab(m.out1, un = FALSE)$Observations["Matched (ESS)", "Treated"],  format = "f", digits = 0, big.mark = ",")
ess_control1  <- formatC(cobalt::bal.tab(m.out1, un = FALSE)$Observations["Matched (ESS)", "Control"],  format = "f", digits = 0, big.mark = ",")
```

### analysis 

```{r}
vars_rr <- c(
  "BirthTerminationYear",
  "I(BirthTerminationYear ^ 2)",
  "Mom_Age",
  "LOPC",
  "Bedouin",
  "NSAID_indication",
  "Diabetes",
  "PregnancyNum",
  "obesity",
  "folic_acid",
  "Smoker"
)


maj_df_removing <- rr_summery_cus(
  first_trimester_exposure_any,
  Congenital_Malformations_Major,
  vars_rr,
  m.data1,
  cluster_col = "MPatientIdentity"
)

cvs_df_removing <- rr_summery_cus(
  first_trimester_exposure_any,
  CVS_Malformations,
  vars_rr,
  m.data1,
  cluster_col = "MPatientIdentity"
)

msk_df_removing <- rr_summery_cus(
  first_trimester_exposure_any,
  MSK_Malformations,
  vars_rr,
  m.data1,
  cluster_col = "MPatientIdentity"
)

neuro_df_removing <- rr_summery_cus(
  first_trimester_exposure_any,
  NEURO_Malformations,
  vars_rr,
  m.data1,
  cluster_col = "MPatientIdentity"
)

clp_df_removing <- rr_summery_cus(
  first_trimester_exposure_any,
  CleftPalate_Malformations,
  vars_rr,
  m.data1,
  cluster_col = "MPatientIdentity"
)

gi_df_removing <- rr_summery_cus(
  first_trimester_exposure_any,
  GI_Malformations,
  vars_rr,
  m.data1,
  cluster_col = "MPatientIdentity"
)

gu_df_removing <- rr_summery_cus(
  first_trimester_exposure_any,
  UG_Malformations,
  vars_rr,
  m.data1,
  cluster_col = "MPatientIdentity"
)

m1_est_df <- bind_rows(
  maj_df_removing,
  cvs_df_removing,
  msk_df_removing,
  neuro_df_removing,
  clp_df_removing,
  gi_df_removing,
  gu_df_removing
) %>%
  transmute(malformation,
         m1_est = est_ci(adj_wts_rr, adj_wts_rr_low, adj_wts_rr_high))

m1_est_df
```


## replacing "other antipyretics before NSAIDs" in the model

### matching 

```{r wrangling before other anypiretics and matching}
m.out2 <- matchit(
  first_trimester_exposure_any ~
    BirthTerminationYear +
    I(BirthTerminationYear^2) +
    Mom_Age +
    LOPC +
    Bedouin +
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker +
    other_antipyretics_before_NSAIDs,
  data = clean_df_excluded,
  method = "quick",
  estimand = "ATE"
)

m.data2 <- match.data(m.out2) |>
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

ess_treated2  <- formatC(cobalt::bal.tab(m.out2, un = FALSE)$Observations["Matched (ESS)", "Treated"],  format = "f", digits = 0, big.mark = ",")
ess_control2  <- formatC(cobalt::bal.tab(m.out2, un = FALSE)$Observations["Matched (ESS)", "Control"],  format = "f", digits = 0, big.mark = ",")
```

### analysis 

```{r}
vars_rr <- c(
  "BirthTerminationYear",
  "I(BirthTerminationYear ^ 2)",
  "Mom_Age",
  "LOPC",
  "Bedouin",
  "NSAID_indication",
  "Diabetes",
  "PregnancyNum",
  "obesity",
  "folic_acid",
  "Smoker",
  "other_antipyretics_before_NSAIDs"
)


maj_df_before <- rr_summery_cus(
  first_trimester_exposure_any,
  Congenital_Malformations_Major,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

cvs_df_before <- rr_summery_cus(
  first_trimester_exposure_any,
  CVS_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

msk_df_before <- rr_summery_cus(
  first_trimester_exposure_any,
  MSK_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

neuro_df_before <- rr_summery_cus(
  first_trimester_exposure_any,
  NEURO_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

clp_df_before <- rr_summery_cus(
  first_trimester_exposure_any,
  CleftPalate_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

gi_df_before <- rr_summery_cus(
  first_trimester_exposure_any,
  GI_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

gu_df_before <- rr_summery_cus(
  first_trimester_exposure_any,
  UG_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

m2_est_df <- bind_rows(
  maj_df_before,
  cvs_df_before,
  msk_df_before,
  neuro_df_before,
  clp_df_before,
  gi_df_before,
  gu_df_before
) %>%
  transmute(malformation,
         m2_est = est_ci(adj_wts_rr, adj_wts_rr_low, adj_wts_rr_high))

m2_est_df
```


## replacing "other antipyretics before NSAIDs" and adding "other antipyretics after NSAIDs" to the model

### analysis 

```{r}
vars_rr <- c(
  "BirthTerminationYear",
  "I(BirthTerminationYear ^ 2)",
  "Mom_Age",
  "LOPC",
  "Bedouin",
  "NSAID_indication",
  "Diabetes",
  "PregnancyNum",
  "obesity",
  "folic_acid",
  "Smoker",
  "other_antipyretics_before_NSAIDs",
  "other_antipyretics_after_NSAIDs"
)

maj_df_before_after <- rr_summery_cus(
  first_trimester_exposure_any,
  Congenital_Malformations_Major,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

cvs_df_before_after <- rr_summery_cus(
  first_trimester_exposure_any,
  CVS_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

msk_df_before_after <- rr_summery_cus(
  first_trimester_exposure_any,
  MSK_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

neuro_df_before_after <- rr_summery_cus(
  first_trimester_exposure_any,
  NEURO_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

clp_df_before_after <- rr_summery_cus(
  first_trimester_exposure_any,
  CleftPalate_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

gi_df_before_after <- rr_summery_cus(
  first_trimester_exposure_any,
  GI_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

gu_df_before_after <- rr_summery_cus(
  first_trimester_exposure_any,
  UG_Malformations,
  vars_rr,
  m.data2,
  cluster_col = "MPatientIdentity"
)

m3_est_df <- bind_rows(
  maj_df_before_after,
  cvs_df_before_after,
  msk_df_before_after,
  neuro_df_before_after,
  clp_df_before_after,
  gi_df_before_after,
  gu_df_before_after
) %>%
  transmute(malformation,
         m3_est = est_ci(adj_wts_rr, adj_wts_rr_low, adj_wts_rr_high))

m3_est_df
```

## Fill In

```{r}
tbl3 <- m.data2 %>%
  select(
    first_trimester_exposure_any_lbl,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations
      ) ~ "dichotomous"
    ),
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  )


tbl3_df <- tbl3 %>% as.data.frame()

names(tbl3_df)[1] <- "malformation"

tbl3_df <- tbl3_df %>%
  left_join(m1_est_df, by = "malformation") %>%
  left_join(m2_est_df, by = "malformation") %>%
  left_join(m3_est_df, by = "malformation")



table3_for_print <- tbl3_df
names(table3_for_print)[2] <- "cases_nsaids"
names(table3_for_print)[3] <- "cases_unexposed"

table3_gt <- gt(table3_for_print, rowname_col = "malformation") |>
  cols_label(
    malformation = md("**Malformation**"),
    cases_nsaids = md(paste0(
      "**NSAID** <br>(N=", table(tbl3$inputs$data[[tbl3$inputs$by]])[1], ")"
    )),
    cases_unexposed = md(paste0(
      "**Unexposed** <br>(N=", table(tbl3$inputs$data[[tbl3$inputs$by]])[2], ")"
    )),
    m1_est = "Model 1",
    m2_est = "Model 2",
    m3_est = "Model 3"
  ) |>
  tab_style(style = cell_text(align = "center"),
            locations = cells_column_labels(columns = everything())) |>
  tab_spanner(label = md("**RR** [95% CI]"),
              columns = c(m1_est, m2_est, m3_est)) |>
  cols_align(
    align = "left",
    columns = c(cases_unexposed, cases_nsaids, m1_est, m2_est, m3_est)
  ) |>
  tab_stub_indent(
    rows = c(
      "Cardiovascular",
      "Musculoskeletal",
      "Cleft palate",
      "Central nervous system",
      "Gastrointestinal",
      "Genitourinary"
    ),
    indent = 3
  )  %>%
  tab_source_note(
    source_note = md(
      "ATE, Average Treatment Effect; ESS, Effective Sample Size; NSAIDS, Nonsteroidal anti-inflammatory drugs."
    )
  ) %>%
    tab_source_note(
    source_note = md(
      "Model 1 was matched and adjusted for birth termination year and its quadratic term, maternal age, pregnancy number, lack of prenatal care, Bedouin population group, NSAID indication, and maternal diabetes, obesity, folic acid use, and smoking. Model 2 included all Model 1 covariates, with additional matching and adjustment for exposure to other antipyretics before NSAID exposure. Model 3 used the same design as Model 2, with additional adjustment, but not matching, for exposure to other antipyretics after NSAID exposure."
    )
  ) %>%
  tab_footnote(footnote = md(
    paste0(
      "ESS for matching-adjusted model targeting the ATE were ",
      ess_treated1,
      " exposed and ",
      ess_control1,
      " controls. No actual units were discarded during the proccess."
    )
  ),
  locations = cells_column_labels(columns = m1_est)) %>%
  tab_footnote(footnote = md(
    paste0(
      "ESS for matching-adjusted model targeting the ATE were ",
      ess_treated2,
      " exposed and ",
      ess_control2,
      " controls. No actual units were discarded during the proccess."
    )
  ),
  locations = cells_column_labels(columns = c(m2_est, m3_est)))

table3_gt
```



## exluding other antipyretics

### matching 

```{r wrangling exclusion other anypiretics and matching}
m.out4 <- matchit(
  first_trimester_exposure_any ~
    BirthTerminationYear +
    I(BirthTerminationYear^2) +
    Mom_Age +
    LOPC +
    Bedouin +
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker,
  data = (
    clean_df_excluded %>% filter(
      first_trimester_exposure_other_antipyretics == 0
    )
  ),
  method = "quick",
  estimand = "ATE"
)

m.data4 <- match.data(m.out4) |>
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

ess_treated4  <- formatC(cobalt::bal.tab(m.out4, un = FALSE)$Observations["Matched (ESS)", "Treated"],  format = "f", digits = 0, big.mark = ",")
ess_control4  <- formatC(cobalt::bal.tab(m.out4, un = FALSE)$Observations["Matched (ESS)", "Control"],  format = "f", digits = 0, big.mark = ",")
```


### analysis 

```{r}
vars_rr <- c(
  "BirthTerminationYear",
  "I(BirthTerminationYear ^ 2)",
  "Mom_Age",
  "LOPC",
  "Bedouin",
  "NSAID_indication",
  "Diabetes",
  "PregnancyNum",
  "obesity",
  "folic_acid",
  "Smoker"
)


maj_df_exluding <- rr_summery_cus(
  first_trimester_exposure_any,
  Congenital_Malformations_Major,
  vars_rr,
  m.data4,
  cluster_col = "MPatientIdentity"
)

cvs_df_exluding <- rr_summery_cus(
  first_trimester_exposure_any,
  CVS_Malformations,
  vars_rr,
  m.data4,
  cluster_col = "MPatientIdentity"
)

msk_df_exluding <- rr_summery_cus(
  first_trimester_exposure_any,
  MSK_Malformations,
  vars_rr,
  m.data4,
  cluster_col = "MPatientIdentity"
)

neuro_df_exluding <- rr_summery_cus(
  first_trimester_exposure_any,
  NEURO_Malformations,
  vars_rr,
  m.data4,
  cluster_col = "MPatientIdentity"
)

clp_df_exluding <- rr_summery_cus(
  first_trimester_exposure_any,
  CleftPalate_Malformations,
  vars_rr,
  m.data4,
  cluster_col = "MPatientIdentity"
)

gi_df_exluding <- rr_summery_cus(
  first_trimester_exposure_any,
  GI_Malformations,
  vars_rr,
  m.data4,
  cluster_col = "MPatientIdentity"
)

gu_df_exluding <- rr_summery_cus(
  first_trimester_exposure_any,
  UG_Malformations,
  vars_rr,
  m.data4,
  cluster_col = "MPatientIdentity"
)

m4_est_df <- bind_rows(
  maj_df_exluding,
  cvs_df_exluding,
  msk_df_exluding,
  neuro_df_exluding,
  clp_df_exluding,
  gi_df_exluding,
  gu_df_exluding
) %>%
  transmute(malformation,
         m4_est = est_ci(adj_wts_rr, adj_wts_rr_low, adj_wts_rr_high))

m4_est_df
```

## Fill In
```{r}
tbl4 <- m.data4 %>%
  select(
    first_trimester_exposure_any_lbl,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_any_lbl,
    type = list(
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations
      ) ~ "dichotomous"
    ),
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  )


tbl4_df <- tbl4 %>% as.data.frame()

names(tbl4_df)[1] <- "malformation"

tbl4_df <- tbl4_df %>%
  left_join(m4_est_df, by = "malformation")



table4_for_print <- tbl4_df
names(table4_for_print)[2] <- "cases_nsaids"
names(table4_for_print)[3] <- "cases_unexposed"

table4_gt <- gt(
  table4_for_print,
  rowname_col = "malformation"
) |>
  cols_label(
    malformation = md("**Malformation**"),
    cases_nsaids = md(paste0(
      "**NSAID** <br>(N=", table(tbl4$inputs$data[[tbl4$inputs$by]])[1], ")"
    )),
    cases_unexposed = md(paste0(
      "**Unexposed** <br>(N=", table(tbl4$inputs$data[[tbl4$inputs$by]])[2], ")"
    )),
    m4_est = md("**RR** [95% CI]")
  ) |>
  tab_style(style = cell_text(align = "center"),
            locations = cells_column_labels(columns = everything())) |>
  cols_align(
    align = "left",
    columns = c(
      cases_unexposed,
      cases_nsaids,
      m4_est
    )
  ) |>
  tab_stub_indent(
    rows = c(
      "Cardiovascular",
      "Musculoskeletal",
      "Cleft palate",
      "Central nervous system",
      "Gastrointestinal",
      "Genitourinary"
    ),
    indent = 3
  ) %>%
  tab_source_note(
    source_note = md(paste0("Effective sample size for matching-adjusted model targeting the average treatment effect were ", ess_treated4, " exposed and ", ess_control4, " controls. No actual units were discarded during the proccess.")
    )) %>%
  tab_source_note(
    source_note = "The model was matched and adjusted for birth termination year and its quadratic term, maternal age, pregnancy number, lack of prenatal care, Bedouin population group, NSAID indication, and maternal diabetes, obesity, folic acid use, and smoking, only after the exclusion of all pregnencies exposed to other antipyretics")

table4_gt
```

------------------------------------------------------------------------

# Technical Details

## Save objects

```{r, eval=TRUE}
all_pop_tbl1 <- table1 %>% as_gt()
all_matched_tbl1 <- tbl1
all_table1_ddd <- table1_ddd %>% as_gt()
all_ddd_table <- ddd_table
all_love_plot <- love_plot
all_msummary <- m.summary
all_tbl2_df <- tbl2_df
all_nsaid_indication_tbl <- nsaid_indication_tbl
all_table3_gt <- table3_gt
all_table4_gt <- table4_gt

save(
  all_matched_tbl1,
  all_ddd_table,
  all_tbl2_df,
  file = "main.Rda"
)

save(
  all_pop_tbl1,
  all_table1_ddd,
  all_love_plot,
  all_msummary,
  all_nsaid_indication_tbl,
  all_table3_gt,
  all_table4_gt,
  file = "supp.Rda"
)
```


## R Session Info:

```{r}
sessionInfo()
```
