---
title: "NSAIDS in pregnancy - piroxicam"
author: "Ariel A Hasidim"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: yes
    number_sections: yes
    toc_float: yes
    toc_collapsed: yes
    toc_depth: 3
    theme: simplex
---
# Meta
## setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = TRUE, message = TRUE) 

set.seed(54321)

# Installs pacman ("package manager") if needed
if (!require("pacman"))
  install.packages("pacman")

pacman::p_load(
  pacman,
  tidyverse,
  readr,
  gtsummary,
  readxl,
  labelled,
  MatchIt,
  marginaleffects,
  gt,
  gtExtras,
  tidysmd,
  AER,
  cards
) 
```

## wrangling
```{r matching, include=FALSE}
##### GET DATA
raw_df <- read.csv('../NSAIDS_Other_Antipyretics_Sensitivity.csv') %>%
  left_join(read.csv('../paracetamol id.csv'), by = "AdminNum") %>%
  left_join(read.csv('../dipyron id.csv'), by = "AdminNum")


# assigning labels from csv file
metadata <- read_excel("../metadata.xlsx") |> deframe()

##### DATA WRANGLING
clean_df <- raw_df %>%
  mutate(
    MPatientIdentity = if_else(
      is.na(MPatientIdentity),
      AdminNum+30000000,
      MPatientIdentity
    ),
    Congenital_Malformations_Major = if_else(
      is.na(Congenital_Malformations_Major),
      if_else(
        CVS_Malformations +
          MSK_Malformations +
          NEURO_Malformations +
          CleftPalate_Malformations +
          GI_Malformations +
          UG_Malformations > 0,
        1,
        0
      ),
      Congenital_Malformations_Major
    ),
    SexCode = case_when(SexCode == "Male" ~ 1, SexCode == "Female" ~ 0, .default = NA),
    Diabetes = replace_na(Diabetes, 0),
    pregestational_diabetes = if_else((Diabetes == 1) & (Gestational_Diabetes == 0), 1, 0),
    Smoker = replace_na(Smoker, 0),
    LOPC = replace_na(LOPC, 0),
    PregnancyTermination = as.integer(PregnancyTermination),
    BirthYearGroup = cut(
      BirthTerminationYear,
      breaks = seq(1998, 2017 + 1, by = 5),
      right = FALSE,
      labels = c("1998–2002", "2003–2007", "2008–2012", "2013–2017")
    ),
    Mom_Age_Group = cut(
      Mom_Age,
      breaks = c(-Inf, 19, 24, 29, 34, 39, 44, Inf),
      right = TRUE,
      labels = c("<20", "20–24", "25–29", "30–34", "35–39", "40–44", "≥45")
    ),
    first_trimester_exposure_any = (
      if_else(
        first_trimester_exposure_Piroxicam + first_trimester_exposure_Diclofenac +
          first_trimester_exposure_Naproxen + first_trimester_exposure_Indometacin +
          first_trimester_exposure_Etodolac + first_trimester_exposure_Piroxicam +
          first_trimester_exposure_Lornoxicam > 0,
        1,
        0
      )
    ),
    first_trimester_exposure_other_then_piroxicam = (
      if_else(
          first_trimester_exposure_Diclofenac +
          first_trimester_exposure_Naproxen + first_trimester_exposure_Indometacin +
          first_trimester_exposure_Etodolac + first_trimester_exposure_Piroxicam +
          first_trimester_exposure_Lornoxicam > 0,
        1,
        0
      )
    ),
    first_trimester_exposure_Piroxicam_other_na = 
      case_when(first_trimester_exposure_Piroxicam == 1 ~ 1,
                first_trimester_exposure_other_then_piroxicam == 1 ~ NA,
                .default = first_trimester_exposure_Piroxicam),
    first_trimester_exposure_Piroxicam_lbl = if_else(first_trimester_exposure_Piroxicam == 0, "Unexposed", "Piroxicam"),
    first_trimester_exposure_other_antipyretics = if_else(first_trimester_exposure_Paracetamol + first_trimester_exposure_Dipyrone > 0, 1, 0),
    PregnancyNum = if_else(PregnancyNum > 25, NA, PregnancyNum),
    ddd_class_piroxicam = factor(case_when(
      first_trimester_DDD_Piroxicam > 21 ~ 3,
      first_trimester_DDD_Piroxicam > 7 ~ 2,
      first_trimester_DDD_Piroxicam >= 1 ~ 1,
      .default = 0
    )),
    ddd_class_diclofenac = factor(case_when(
      first_trimester_DDD_Diclofenac > 21 ~ 3,
      first_trimester_DDD_Diclofenac > 7 ~ 2,
      first_trimester_DDD_Diclofenac >= 1 ~ 1,
      .default = 0
    ))
    ,
    ddd_class_naproxen = factor(case_when(
      first_trimester_DDD_Naproxen > 21 ~ 3,
      first_trimester_DDD_Naproxen > 7 ~ 2,
      first_trimester_DDD_Naproxen >= 1 ~ 1,
      .default = 0
    )),
    ddd_class_indometacin = factor(case_when(
      first_trimester_DDD_Indometacin > 21 ~ 3,
      first_trimester_DDD_Indometacin > 7 ~ 2,
      first_trimester_DDD_Indometacin >= 1 ~ 1,
      .default = 0
    )),
    ddd_class_etodolac = factor(case_when(
      first_trimester_DDD_Etodolac > 21 ~ 3,
      first_trimester_DDD_Etodolac > 7 ~ 2,
      first_trimester_DDD_Etodolac >= 1 ~ 1,
      .default = 0
    )),
    ddd_class_piroxicam = factor(case_when(
      first_trimester_DDD_Piroxicam > 21 ~ 3,
      first_trimester_DDD_Piroxicam > 7 ~ 2,
      first_trimester_DDD_Piroxicam >= 1 ~ 1,
      .default = 0
    )),
    ddd_class_lornoxicam = factor(case_when(
      first_trimester_DDD_Lornoxicam > 21 ~ 3,
      first_trimester_DDD_Lornoxicam > 7 ~ 2,
      first_trimester_DDD_Lornoxicam >= 1 ~ 1,
      .default = 0
    )) 
  )

clean_df <- clean_df |> 
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

clean_df_excluded <- clean_df %>%
  transmute(first_trimester_exposure_Piroxicam,
    first_trimester_exposure_Piroxicam_lbl,
    MPatientIdentity,
    first_trimester_exposure_Paracetamol,
    first_trimester_exposure_Dipyrone,
    first_trimester_exposure_other_antipyretics,
    first_trimester_exposure_Piroxicam_lbl,
    New_MomAge,
    Mom_Age,
    Mom_Age_Group,
    Bedouin,
    pregnancy_termination,
    LOPC,
    PregnancyAge_Final,
    Smoker,
    Diabetes,
    pregestational_diabetes,
    Gestational_Diabetes,
    SexCode,
    NSAID_indication,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations,
    PregnancyTermination,
    BirthTerminationYear,
    BirthYearGroup,
    Perinatal_Death,
    LBW,
    VLBW,
    Apgar1,
    Apgar5,
    InfantWeigth,
    PregnancyNum,
    obesity,
    folic_acid,
    fertilitytx,
    insemination,
    ivf
    ) %>%
  drop_na(
    Mom_Age,
        Bedouin,
        PregnancyNum,
        LOPC,
        NSAID_indication,
        BirthTerminationYear,
        Diabetes,
        obesity,
        folic_acid,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
    UG_Malformations
  )

 
clean_df_excluded <- clean_df_excluded |> 
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

```
## functions
```{r functions}
est_ci <- function(est, low, high) {
  paste0(round(est, 2), " [", round(low, 2), ", ", round(high, 2), "]")
}

rr_summery_cus <- function(
    exposure,                       # bare column (e.g., first_trimester_exposure_Piroxicam)
    outcome,                        # bare column (e.g., Congenital_Malformations_Major)
    vars,                           # character vector of adjustment terms
    data,                           # data.frame / tibble
    family = poisson(link = "log"),
    unexposed_label = "unexposed",
    exposed_label   = "nsaids",
    wts_col = "weights",
    cluster_col = NA
) {
  expo <- deparse1(substitute(exposure))
  outc <- deparse1(substitute(outcome))

  # label fallback
  out_label <- tryCatch({
    lab <- labelled::var_label(data[[outc]])
    if (is.null(lab) || identical(lab, "")) outc else as.character(lab)
  }, error = function(e) outc)

  # --- helpers ---
  expo_factorize <- function(df, prefix, pred_df) {
    pred_df %>%
      transmute(
        "{expo}" := .data[[expo]],
        .grp = if_else(.data[[expo]] == 0, unexposed_label, exposed_label),
        "{prefix}_incidence"      := estimate * 1000,
        "{prefix}_incidence_low"  := conf.low * 1000,
        "{prefix}_incidence_high" := conf.high * 1000
      ) %>%
      select(.grp, starts_with(paste0(prefix, "_"))) %>%
      pivot_wider(
        names_from = .grp,
        values_from = c(
          any_of(paste0(prefix, c("_incidence","_incidence_low","_incidence_high")))
        )
      )
  }

  rr_cols <- function(prefix, cmp_df) {
    cmp_df %>%
      transmute(
        "{prefix}_rr"      := estimate,
        "{prefix}_rr_low"  := conf.low,
        "{prefix}_rr_high" := conf.high
      )
  }

  # --- formulas ---
  f_unadj <- reformulate(expo, response = outc)
  f_adj   <- reformulate(c(expo, vars), response = outc)

  # --- 1) Unadjusted ---
  fit_unadj <- glm(f_unadj, data = data, family = family)

  pred_unadj <- avg_predictions(fit_unadj, variables = expo)
  cmp_unadj  <- avg_comparisons(fit_unadj, variables = expo, comparison = "lnratioavg", transform = "exp")

  out_tbl <- bind_cols(
    expo_factorize(data, "unadj", pred_unadj),
    rr_cols("unadj", cmp_unadj)
  )

  # --- 2) Adjusted ---
  fit_adj <- glm(f_adj, data = data, family = family)

  pred_adj <- avg_predictions(fit_adj, variables = expo, type = "response")
  
  cmp_adj  <- avg_comparisons(
    fit_adj,
    variables = expo,
    type = "response",
    comparison = "lnratioavg",
    transform = "exp",
    vcov = if (is.na(cluster_col)) "HC3" else as.formula(paste0("~", cluster_col))
  )
  
  out_tbl <- out_tbl %>%
    bind_cols(
      expo_factorize(data, "adj", pred_adj),
      rr_cols("adj", cmp_adj)
    )

  # --- 3) Adjusted + weights (if available) ---
  has_w <- (wts_col %in% names(data))
  has_c <- (!is.na(cluster_col))

  if (has_w) {
    fit_w <- glm(f_adj, data = data, family = family, weights = data[[wts_col]])
    
    vcov_arg <- if (has_c) as.formula(paste0("~subclass + ", cluster_col)) else ~subclass

    pred_w <- avg_predictions(
      fit_w,
      variables = expo,
      type = "response",
      vcov = vcov_arg,
      wts  = if (has_c) FALSE else wts_col
    )

    cmp_w <- avg_comparisons(
      fit_w,
      variables = expo,
      type = "response",
      comparison = "lnratioavg",
      transform = "exp",
      vcov = vcov_arg,
      wts  = if (has_c) FALSE else wts_col
    )
    
    out_tbl <- out_tbl %>%
      bind_cols(
        expo_factorize(data, "adj_wts", pred_w),
        rr_cols("adj_wts", cmp_w)
      )
  } else {
    empty_w <- tibble(
      adj_wts_incidence_unexposed = NA_real_,
      adj_wts_incidence_nsaids    = NA_real_,
      adj_wts_incidence_low_unexposed = NA_real_,
      adj_wts_incidence_low_nsaids    = NA_real_,
      adj_wts_incidence_high_unexposed = NA_real_,
      adj_wts_incidence_high_nsaids    = NA_real_,
      adj_wts_rr = NA_real_,
      adj_wts_rr_low = NA_real_,
      adj_wts_rr_high = NA_real_
    )
    out_tbl <- bind_cols(out_tbl, empty_w)
  }

  out_tbl %>% mutate(malformation = out_label)
}
```

# Population
all cases, including missings

## Table1
```{r}
table1 <- clean_df %>%
  transmute (
    first_trimester_exposure_Piroxicam_lbl,
    BirthTerminationYear = BirthYearGroup,
    Mom_Age = Mom_Age_Group,
    Bedouin,
    obesity,
    Smoker,
    Diabetes,
    NSAID_indication,
    first_trimester_exposure_other_antipyretics,
    PregnancyNum,
    PregnancyAge_Final,
    fertilitytx,
    insemination,
    ivf,
    LOPC,
    folic_acid,
    SexCode,
    pregnancy_termination,
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_Piroxicam_lbl,
    type = list(
      c() ~ "continuous",
      c(BirthTerminationYear, Mom_Age) ~ "categorical",
      c(
        Bedouin,
        Smoker,
        Diabetes,
        SexCode,
        LOPC,
        pregnancy_termination,
        NSAID_indication,
        obesity,
        folic_acid,
        fertilitytx,
        insemination,
        ivf,
        first_trimester_exposure_other_antipyretics
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(PregnancyAge_Final, PregnancyNum) ~ "{median} ({p25}, {p75})"
    ),
    missing = "ifany",
    missing_text = "Missing"
  )  %>%
  add_p() %>%
  bold_labels() %>%
  modify_indent(columns = label,
                rows = variable %in% c("insemination", "ivf"))

table1
```

## Table2
```{r}
table2 <- clean_df %>%
  select(
    first_trimester_exposure_Piroxicam,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_Piroxicam,
    type = list(
      c() ~ "continuous",
      c() ~ "categorical",
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations,
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c() ~ "{median} ({p25}, {p75})"
    ),
    missing = "no"
  ) %>%
  add_n() %>%
  add_p()

table2
```


## Multivar for "Major Malformations", no matching

### Assesing overdispersion:

This is the the source for the method with refrences:

-   <https://stats.stackexchange.com/a/66593/323174>

```{r}
# For poisson model
rd <- glm(Congenital_Malformations_Major ~ 1, data = clean_df, family = poisson(link = "log"))
dispersiontest(rd,trafo=1) # should have insignificant p-value
```

### Poisson with log link 

summary:

```{r}
m1.fit <-
  glm(
    Congenital_Malformations_Major ~ first_trimester_exposure_Piroxicam +
    BirthTerminationYear +
    I(BirthTerminationYear ^ 2) +
    Mom_Age + 
    LOPC +
    Bedouin + 
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker +
    first_trimester_exposure_other_antipyretics,
    data = clean_df,
    family = poisson(link = "log") # account for OVERDISPERSION in BINARY outcome
  )

summary(m1.fit)
```

full regression (exponentiated = OR):
```{r}
tbl_regression(m1.fit, exponentiate = TRUE)
```


marginal RR effect: <!-- <= botton line -->
```{r}
avg_comparisons(
  m1.fit,
  variables = "first_trimester_exposure_Piroxicam",
  type = "response", # <- doesnt make any change
  comparison = "lnratioavg",
  transform = "exp",
  vcov = ~ MPatientIdentity
)
```

## DDD

### Table1
```{r}
table1_ddd <- clean_df %>%
  select(
    ddd_class_piroxicam,
    BirthYearGroup,
    Mom_Age_Group,
    Bedouin,
    obesity,
    Smoker,
    Diabetes,
    NSAID_indication,
    first_trimester_exposure_other_antipyretics,
    PregnancyNum,
    PregnancyAge_Final,
    fertilitytx,
    insemination,
    ivf,
    LOPC,
    folic_acid,
    SexCode,
    pregnancy_termination,
  ) %>%
  tbl_summary(
    by = ddd_class_piroxicam,
    type = list(
      c() ~ "continuous",
      c(BirthYearGroup, Mom_Age_Group) ~ "categorical",
      c(
        Bedouin,
        Smoker,
        Diabetes,
        SexCode,
        LOPC,
        pregnancy_termination,
        NSAID_indication,
        obesity,
        folic_acid,
        fertilitytx,
        insemination,
        ivf,
        first_trimester_exposure_other_antipyretics
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(PregnancyAge_Final, PregnancyNum) ~ "{median} ({p25}, {p75})"
    ),
    missing = "ifany",
    missing_text = "Missing"
  )  %>%
  add_p(
    test = list(
      all_continuous() ~ "kruskal.test",
      all_categorical() ~ "fisher.test"
    ),
    test.args = list(
      all_tests("fisher.test") ~ list(simulate.p.value = TRUE, B = 10000)
    )
  )

table1_ddd
```

### Analysis

```{r}
m.fit <-
  glm(
    Congenital_Malformations_Major ~ ddd_class_piroxicam + 
    BirthTerminationYear +
    I(BirthTerminationYear ^ 2) +
    Mom_Age + 
    LOPC +
    Bedouin + 
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker +
    first_trimester_exposure_other_antipyretics,
    data = clean_df,
    family = poisson(link = "log")
  )

rx <- "mean\\((\\d+)\\)\\s*/\\s*mean\\(0\\)"

ddd_rr_df <- avg_comparisons(
      m.fit,
      variables  = "ddd_class_piroxicam",
      type = "response",
      comparison = "lnratioavg",
      transform = "exp",
      vcov = ~HC3 + MPatientIdentity
    ) %>%
      as.data.frame() %>%
      transmute(
        class = str_match(contrast, rx)[, 2],
        estimate = estimate,
        p.value  = p.value,
        conf.low = conf.low,
        conf.high = conf.high
      ) %>%
      bind_rows(
        tibble(
          class = "0",
          estimate = 1,
          `2.5 %` = NA_real_,
          `97.5 %` = NA_real_,
          `Pr(>|z|)` = NA_real_
        )
      )

ddd_table <- clean_df %>%
  select(Congenital_Malformations_Major, ddd_class_piroxicam) %>%
  summarise(
    .by = ddd_class_piroxicam,
    n = sum(Congenital_Malformations_Major == 1, na.rm = TRUE),
    total = sum(!is.na(Congenital_Malformations_Major)),
    pct   = 100 * n / total,
    label = sprintf("%d/%d (%.1f%%)", n, total, pct)
  ) %>%
  transmute(class = ddd_class_piroxicam, Congenital_Malformations_Major = label) %>%
  left_join(ddd_rr_df,
  by = join_by(class)) %>%
  arrange(class) %>%
  transmute(
    class = case_when(
      class == 3 ~ ">21",
      class == 2 ~ "8-21",
      class == 1 ~ "1-7",
      class == 0 ~ "None"
    ),
    Congenital_Malformations_Major,
    aRR = est_ci(estimate, conf.low, conf.high)
  ) %>%
  gt() %>%
  cols_label(
    class = "Total DDD for Piroxicam",
    Congenital_Malformations_Major = "Major Congenital Malformations",
    aRR = "Adjusted RR (%95 CI)"
  )

ddd_table
```


# Matched Cohort

## Matching
```{r}
# Mahalanobis distance, 1:1 nearest neighbor matching with no replacement
m.out <- matchit(
  first_trimester_exposure_Piroxicam ~ 
    BirthTerminationYear +
    I(BirthTerminationYear ^ 2) +
    Mom_Age + 
    LOPC +
    Bedouin + 
    NSAID_indication +
    Diabetes +
    PregnancyNum +
    obesity +
    folic_acid +
    Smoker +
    first_trimester_exposure_other_antipyretics,
  data = clean_df_excluded,
  method = "quick",
  estimand = "ATE"
)

m.data <- match.data(m.out) |>
  labelled::set_variable_labels(!!!metadata, .strict = FALSE)

ess_treated  <- formatC(cobalt::bal.tab(m.out, un = FALSE)$Observations["Matched (ESS)", "Treated"],  format = "f", digits = 0, big.mark = ",")
ess_control  <- formatC(cobalt::bal.tab(m.out, un = FALSE)$Observations["Matched (ESS)", "Control"],  format = "f", digits = 0, big.mark = ",")
```

## Assessing the Quality Excluded and Matched Cohort

Model specifications:

```{r}
m.out
```

Summary:

```{r, cache=TRUE}
# Checking balance before and after matching:
m.summary <- summary(m.out, un = TRUE)

m.summary
```


### Love Plot

```{r, cache=TRUE, eval=TRUE}
cobalt::love.plot(m.out, binary = "std", thresholds = c(m = .1))
```

## Table 1

```{r}
# Variables of interest
vars <- c(
  "first_trimester_exposure_Piroxicam",
  "Mom_Age",
  "Bedouin",
  "PregnancyNum",
  "LOPC",
  "Diabetes",
  "SexCode",
  "pregnancy_termination",
  "BirthTerminationYear",
  "NSAID_indication",
  "obesity",
  "folic_acid",
  "Smoker",
  "SexCode",
  "pregestational_diabetes",
  "fertilitytx",
  "insemination",
  "ivf",
  "PregnancyAge_Final",
  "first_trimester_exposure_other_antipyretics"
)

# SMDs before matching
smds <- tidy_smd(
  .df = m.data,
  .vars = vars,
  .group = first_trimester_exposure_Piroxicam,
  .wts = weights,
  include_observed = TRUE,
  na.rm = TRUE
) %>%
  select(-first_trimester_exposure_Piroxicam) %>%
  pivot_wider(names_from = method, values_from = smd) %>%
  mutate(
    before = abs(observed),
    after = abs(weights),
    .keep = "unused"
  )

tbl1 <- m.data %>%
  transmute (
    first_trimester_exposure_Piroxicam_lbl,
    BirthTerminationYear = BirthYearGroup,
    Mom_Age = Mom_Age_Group,
    Bedouin,
    obesity,
    Smoker,
    Diabetes,
    NSAID_indication,
    first_trimester_exposure_other_antipyretics,
    PregnancyNum,
    PregnancyAge_Final,
    fertilitytx,
    insemination,
    ivf,
    LOPC,
    folic_acid,
    SexCode,
    pregnancy_termination,
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_Piroxicam_lbl,
    type = list(
      c() ~ "continuous",
      c(BirthTerminationYear, Mom_Age) ~ "categorical",
      c(
        Bedouin,
        Smoker,
        Diabetes,
        SexCode,
        LOPC,
        pregnancy_termination,
        NSAID_indication,
        obesity,
        folic_acid,
        fertilitytx,
        insemination,
        ivf,
        first_trimester_exposure_other_antipyretics
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(PregnancyAge_Final, PregnancyNum) ~ "{median} ({p25}, {p75})"
    ),
    missing = "ifany",
    missing_text = "Missing"
  )  %>%
  add_p() %>%
  bold_labels() %>%
  modify_table_body(
    ~ .x %>%
      left_join(smds, by = "variable") %>%
      mutate(
        smd_before = if_else(row_type == "label", if_else(is.na(before), "", as.character(round(
          before, 2
        ))), ""),
        smd_after = if_else(row_type == "label", if_else(is.na(after), "", as.character(round(
          after, 2
        ))), "")
      )
  ) %>%
  modify_header(smd_before ~ "**aSMD before**", smd_after ~ "**aSMD after**") %>%
  modify_indent(columns = label,
                rows = variable %in% c("insemination", "ivf")) %>%
modify_footnote_body(
  footnote = "Covariates included in adjusted models",
  columns = "label",
  rows = variable %in% c(
  "BirthTerminationYear",
  "Mom_Age",
  "LOPC",
  "Bedouin",
  "NSAID_indication",
  "Diabetes",
  "PregnancyNum",
  "obesity",
  "Smoker",
      "folic_acid",
      "first_trimester_exposure_Dipyrone",
      "first_trimester_exposure_Paracetamol"
  )
  & row_type == "label"
  ) %>%
  as_gt() %>%
  opt_footnote_marks(marks = c("1", "2", "*"))  %>%
  tab_source_note(
    source_note = md(
      "aSMD, absolute Standardized Mean Difference; ATE, Average Treatment Effect; ESS, Effective Sample Size; NSAIDS, Nonsteroidal anti-inflammatory drugs; Tx, Treatment."
    )
  ) %>%
  tab_source_note(source_note = md(
    paste0(
      "ESS for matching-adjusted model targeting the ATE were ",
      ess_treated,
      " exposed and ",
      ess_control,
      " controls. No actual units were discarded during the proccess."
    )
  )) %>%
  tab_source_note(
    source_note = md(
      "Maternal obesity was defined using ICD-9 codes 278.0–278.4, diabetes using ICD-9 250.* and gestational diabetes (GDM) 648.00–648.04, and folic acid use as dispensation during the first trimester. Maternal smoking was based on self-report or ICD-9 code 305.1. Exposure to other analgesics or antipyretics was defined as first-trimester exposure to either acetaminophen or dipyrone. NSAID indications were defined as first-trimester diagnoses for conditions commonly treated with NSAIDs, including musculoskeletal/joint disorders, pain and inflammatory conditions, injuries/fractures, and pregnancy-related diagnoses such as threatened abortion or fever/infection. Gravidity refers to total prior pregnancies. "
    )
  ) %>%
  tab_source_note(
    source_note = md(
      "Missing values for fetal sex reflect pregnancy terminations due to suspected fetal malformations, for which fetal sex could not be determined."
    )
  ) %>%
  tab_source_note(
    source_note = md(
      "SMDs for *Calendar year of birth* were calculated using the ordinal calendar year variable; grouped categories are shown for presentation purposes only."
    )
)

tbl1
```

## Table 2 (simple)

```{r}
tbl2_simple <- m.data %>%
  select(
    first_trimester_exposure_Piroxicam_lbl,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations,
    Perinatal_Death,
    LBW,
    VLBW,
    Apgar1,
    Apgar5,
    InfantWeigth
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_Piroxicam_lbl,
    type = list(
      c(InfantWeigth) ~ "continuous",
      c() ~ "categorical",
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations,
        Perinatal_Death,
        LBW,
        VLBW,
      ) ~ "dichotomous"
    ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_categorical() ~ "{n} ({p}%)",
      c(Apgar1, Apgar5) ~ "{median} ({p25}, {p75})"
    ),
    missing = "no"
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  add_n()

tbl2_simple
```

## Table 2 - Full adjusted for all systemic malformations

```{r}
vars_rr <- c(
  "BirthTerminationYear",
  "I(BirthTerminationYear ^ 2)",
  "Mom_Age",
  "LOPC",
  "Bedouin",
  "NSAID_indication",
  "Diabetes",
  "PregnancyNum",
  "obesity",
  "folic_acid",
  "Smoker",
  "first_trimester_exposure_other_antipyretics"
)

maj_df <- rr_summery_cus(
  first_trimester_exposure_Piroxicam,
  Congenital_Malformations_Major,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

cvs_df <- rr_summery_cus(
  first_trimester_exposure_Piroxicam,
  CVS_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

msk_df <- rr_summery_cus(
  first_trimester_exposure_Piroxicam,
  MSK_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

neuro_df <- rr_summery_cus(
  first_trimester_exposure_Piroxicam,
  NEURO_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

clp_df <- rr_summery_cus(
  first_trimester_exposure_Piroxicam,
  CleftPalate_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

gi_df <- rr_summery_cus(
  first_trimester_exposure_Piroxicam,
  GI_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)

gu_df <- rr_summery_cus(
  first_trimester_exposure_Piroxicam,
  UG_Malformations,
  vars_rr,
  m.data,
  cluster_col = "MPatientIdentity"
)
```

### Fill In
```{r}
tbl2 <- m.data %>%
  select(
    first_trimester_exposure_Piroxicam_lbl,
    Congenital_Malformations_Major,
    CVS_Malformations,
    MSK_Malformations,
    NEURO_Malformations,
    CleftPalate_Malformations,
    GI_Malformations,
    UG_Malformations
  ) %>%
  tbl_summary(
    by = first_trimester_exposure_Piroxicam_lbl,
    type = list(
      c(
        Congenital_Malformations_Major,
        CVS_Malformations,
        MSK_Malformations,
        NEURO_Malformations,
        CleftPalate_Malformations,
        GI_Malformations,
        UG_Malformations
      ) ~ "dichotomous"
    ),
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  )

tbl2_df <- tbl2 %>% as.data.frame()

names(tbl2_df)[1] <- "malformation"

tbl2_df <- tbl2_df %>%
  left_join((
    bind_rows(maj_df, cvs_df, msk_df, neuro_df, clp_df, gi_df, gu_df)
  ), by = "malformation")

table2_for_print <- tbl2_df
names(table2_for_print)[2] <- "cases_nsaids"
names(table2_for_print)[3] <- "cases_unexposed"

gt(
  table2_for_print %>%
    transmute(
      malformation,
      cases_nsaids,
      unadj_incidence_nsaids_conj = est_ci(
        unadj_incidence_nsaids,
        unadj_incidence_low_nsaids,
        unadj_incidence_high_nsaids
      ),
      cases_unexposed,
      unadj_incidence_unexposed_conj = est_ci(
        unadj_incidence_unexposed,
        unadj_incidence_low_unexposed,
        unadj_incidence_high_unexposed
      ),
      unadj_rr_conj = est_ci(unadj_rr, unadj_rr_low, unadj_rr_high),
      adj_rr_conj = est_ci(adj_rr, adj_rr_low, adj_rr_high),
      adj_wts_rr_conj = est_ci(adj_wts_rr, adj_wts_rr_low, adj_wts_rr_high),
      adj_wts_rr,
      adj_wts_rr_low,
      adj_wts_rr_high
    ),
  rowname_col = "malformation"
) |>
  cols_label(
    malformation = md("**Malformation**"),
    cases_nsaids = "Events",
    unadj_incidence_nsaids_conj = "Events/1000 (95% CI)",
    cases_unexposed = "Events",
    unadj_incidence_unexposed_conj = "Events/1000 (95% CI)",
    unadj_rr_conj = "Unadjusted",
    adj_rr_conj = "Adjusted",
    adj_wts_rr_conj = "Matched Adjusted",
    adj_wts_rr = ""
  ) |>
  tab_style(style = cell_text(align = "center"),
            locations = cells_column_labels(columns = everything())) |>
  tab_spanner(
    label = md(paste0(
      "**Piroxicam** <br>(N=", table(tbl2$inputs$data[[tbl2$inputs$by]])[1], ")"
    )),
    columns = c(cases_nsaids, unadj_incidence_nsaids_conj)
  ) |>
  tab_spanner(
    label = md(paste0(
      "**Unexposed**<br>(N=", table(tbl2$inputs$data[[tbl2$inputs$by]])[2], ")"
    )),
    columns = c(cases_unexposed, unadj_incidence_unexposed_conj)
  ) |>
  tab_spanner(
    label = md("**RR**<br>(95% CI)"),
    columns = c(unadj_rr_conj, adj_rr_conj, adj_wts_rr_conj, adj_wts_rr)
  ) |>
  cols_align(
    align = "left",
    columns = c(
      cases_unexposed,
      unadj_incidence_unexposed_conj,
      cases_nsaids,
      unadj_incidence_nsaids_conj,
      unadj_rr_conj,
      adj_rr_conj,
      adj_wts_rr_conj
    )
  ) |>
  tab_stub_indent(
    rows = c(
      "Cardiovascular",
      "Musculoskeletal",
      "Cleft palate",
      "Central nervous system",
      "Gastrointestinal",
      "Genitourinary"
    ),
    indent = 3
  ) |>
  tab_options(table.width = px(1400)) |>
  fmt_number(drop_trailing_zeros = FALSE) |>
  gt_plt_conf_int(
    adj_wts_rr,
    c(adj_wts_rr_low, adj_wts_rr_high),
    ref_line = 1,
    text_size = 0,
    palette = c("black", "darkgrey", "black", "black")
  ) |>
  cols_hide(columns = c(adj_wts_rr_low, adj_wts_rr_high))
```


------------------------------------------------------------------------

# Technical Details

## Save objects
```{r}
piroxicam_pop_tbl1 <- table1 %>% as_gt()
piroxicam_matched_tbl1 <- tbl1
piroxicam_table1_ddd <- table1_ddd %>% as_gt()
piroxicam_ddd_table <- ddd_table
piroxicam_love_plot <- love_plot
piroxicam_tbl2_df <- tbl2_df

save(
  piroxicam_matched_tbl1,
  piroxicam_ddd_table,
  piroxicam_tbl2_df,
  file = "./piroxicam-main.Rda"
)

save(
  piroxicam_pop_tbl1,
  piroxicam_table1_ddd,
  piroxicam_love_plot,
  file = "piroxicam-supp.Rda"
)
```


## R Session Info:

```{r}
sessionInfo()
```
